\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=1.2cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}

\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=black
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlist[itemize]{
  leftmargin=1.05em,
  itemsep=0pt,
  topsep=1pt,
  parsep=0pt,
  partopsep=0pt
}

\titleformat{\section}{\normalsize\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{2pt}

\newcommand{\entry}[4]{
  \textbf{#1} \hfill {\small #2}\\
  {\small \textit{#3}}\\[-3pt]
  {\small #4}\vspace{-2pt}
}

\newcommand{\compactentry}[3]{
  \textbf{#1} \hfill {\small #2}\\[-3pt]
  {\small #3}\vspace{-2pt}
}

\begin{document}

%==================== HEADER ====================
{\Large \textbf{Yo-Rei Huang / OsGa} \hfill \normalsize 黃宥睿}\\[-1pt]
\textbf{CTF Player \textbar\ Developer \textbar\ Cybersecurity Student}\\[-1pt]
Taiwan, GMT+8 \textbar\
\href{mailto:hi@osga.dev}{hi@osga.dev} \textbar\
\href{https://osga.dev}{osga.dev} \textbar\
\href{https://github.com/OsGa24}{github.com/OsGa24} \textbar\
\href{https://www.linkedin.com/in/osga}{linkedin.com/in/osga}

%==================== SUMMARY ====================
\section*{Summary}
Cybersecurity-focused Information Management student at NYUST. Active CTF player and developer with experience in campus network/system operations, web tooling, CTF education, technical speaking, and attack-defense exercises.

%==================== EDUCATION ====================
\section*{Education}
\compactentry
{National Yunlin University of Science and Technology}
{2024 -- Present}
{B.S., Department of Information Management, AI Elite Program}

%==================== EXPERIENCE ====================
\section*{Experience}
\entry
{National Yunlin University of Science and Technology}
{2025 -- Present}
{System Team Leader / Network Development Student Assistant}
{Led system-side work in the Network Management Team; supported campus network services, system administration, internal tooling, troubleshooting, and technical operations across multiple university units.}

\entry
{National Yunlin University of Science and Technology}
{2024 -- 2026}
{Cybersecurity Division Student Assistant / Programming Teaching Assistant}
{Supported cybersecurity operations at the Library and Information Center; assisted programming course instruction, hands-on practice, and student debugging.}

\entry
{Executive Yuan Cyber Range Exercise}
{2025 -- 2026}
{Red Team Member}
{Participated in cyber attack-and-defense exercises, focusing on attacker-side thinking, vulnerability discovery, and attack-path exploration.}

%==================== PROJECTS ====================
\section*{Selected Projects}
\begin{itemize}
  \item \textbf{\href{https://sitcon.org/2026}{SITCON 2026}} --- Contributed to official websites and event systems, including the main site, field game, CFP pages, and sponsorship materials. Built with Astro, Next.js, Go, and Three.js.
  \item \textbf{\href{https://nyust-ics.osga.dev}{NYUST ICS}} --- NYUST course schedule converter that parses DOCX files into ICS calendar files, with course-time parsing, consecutive-session merging, preview, and browser-side processing.
  \item \textbf{\href{https://github.com/osga24/Quick-Jump}{QuickJump}} --- Bash/Zsh utility for jumping to frequently used directories through custom hotkeys, with shell integration, autocompletion, JSON config, and install scripts.
\end{itemize}

%==================== ACHIEVEMENTS ====================
\section*{Selected Achievements}
\begin{itemize}
  \item \textbf{2026} --- 56th National Skills Competition, Cyber Security Regional: Central Region Honorable Mention; ITSA Generative AI Application Web Design Competition: 3rd Place
  \item \textbf{2025} --- HITCON CTF Elite Exchange Competition: Rank 6; CDX Cybersecurity Attack \& Defense Exchange Competition: Preliminary 2nd / Final Honorable Mention; AIS3 EOF: Best Blue Team Spirit Award; AIS3 HACKATHON: Bronze Award; Information Application Services Innovation Contest: TWM AI Red Team eKYC Track
  \item \textbf{2024} --- AIS3 MyFirstCTF: Silver Award
  \item \textbf{2023} --- 53rd National Skills Competition, Cyber Security Regional: Central Region Honorable Mention
  \item \textbf{2022} --- 52nd National Skills Competition, Information Network Cabling: South Region Gold Medal / National 4th Place
\end{itemize}

%==================== COMMUNITY & TEACHING ====================
\section*{Speaking, Teaching \& Community}
\begin{itemize}
  \item Speaker / instructor on CTF, Linux, web security, Discord bot development, and developer workflows at SITCON, MOPCON, SCIST/SCAICT, AIS3-related activities, and information clubs.
  \item SITCON 2026 Development Team Deputy Lead; TWNOG 7 Infra Team; MOPCON 2025 Development Team; HITCON Event Staff; SITCON Camp 2025 Counselor Team Lead.
  \item AIS3 Juniors Teaching Assistant; SCIST Cybersecurity TA / Problem Setter; THJCC Founder / Problem Setter.
\end{itemize}

%==================== CERTIFICATIONS & SKILLS ====================
\section*{Certifications \& Skills}
\textbf{Certifications:} Cisco Certified Support Technician Cybersecurity; Information Technician Specialist Cybersecurity, both Apr. 13, 2024.\\
\textbf{Security:} CTF, web security, penetration testing basics, attack-defense exercises, cybersecurity training.\\
\textbf{Development:} Python, TypeScript, JavaScript, Shell, Next.js, Astro, FastAPI, Express.js.\\
\textbf{Infrastructure / Network:} Linux administration, Docker services, deployment, monitoring, log investigation, backup/recovery, TCP/IP, DNS, DHCP, NAT, firewall policy, router/switch configuration.

\end{document}
